Nitric-oxide-feedback to ciliary photoreceptor cells orchestrates UV avoidance

### 2023-05-11 Manuscript/Manuscript.Rmd
Update Key resource table

---
title: Nitric-oxide-feedback to ciliary photoreceptor cells orchestrates UV avoidance
  in zooplankton
author: 
  - name: "Kei Jokura<sup>1,`*`</sup>, Nobuo Ueda<sup>2</sup>, Martin Gühmann<sup>3</sup>, Luis Alfonso Yañez-Guerra<sup>1</sup>, Piotr Słowiński<sup>1</sup>, Kyle C. A. Wedgewood<sup>1</sup> and Gáspár Jékely<sup>1,4,`*`</sup>"
    affiliation: "<sup>1</sup>Living Systems Institute, University of Exeter, Stocker road, Exeter, EX4 4QD, United Kingdom <sup>2</sup>Okinawa Institute of Science and Technology, Okinawa, Japan, <sup>3</sup>School of Biological Sciences, University of Bristol, Bristol, United Kingdom, <sup>4</sup>Centre for Organismal Studies (COS), University of Heidelberg, 69120 Heidelberg, Germany  <br> <sup>*</sup>Correspondence`:` kei.jokura @ exeter.ac.uk, gaspar.jekely @ cos.uni-heidelberg.de"
output:
  pdf_document:
    latex_engine: lualatex
    template: default
  html_document:
    theme: lumen
  word_document: default
geometry: left=0.8in,right=0.8in,top=0.8in,bottom=0.5in
mainfont: Arial
monofont: Times New Roman
documentclass: article
classoption: onecolumn
linestretch: 1.2
fontsize: 10pt
bibliography: references.bib
csl: elife.csl
editor_options: 
  markdown: 
    wrap: sentence
---

@@

##Key resources table

```         
library(readxl)
NOSpaper_keyresourcetale <- read_excel("source_data/key_resource_tale.xlsx")

{r echo=FALSE,fig.cap="**Key resources table** "}
```

>>>>

---
title: Nitric-oxide-feedback to ciliary photoreceptor cells orchestrates UV avoidance
  in zooplankton
author: 
  - name: "Kei Jokura<sup>1,`*`</sup>, Nobuo Ueda<sup>2</sup>, Martin Gühmann<sup>3</sup>, Luis Alfonso Yañez-Guerra<sup>1</sup>, Piotr Słowiński<sup>1</sup>, Kyle C. A. Wedgewood<sup>1</sup> and Gáspár Jékely<sup>1,4,`*`</sup>"
    affiliation: "<sup>1</sup>Living Systems Institute, University of Exeter, Stocker road, Exeter, EX4 4QD, United Kingdom <sup>2</sup>Okinawa Institute of Science and Technology, Okinawa, Japan, <sup>3</sup>School of Biological Sciences, University of Bristol, Bristol, United Kingdom, <sup>4</sup>Centre for Organismal Studies (COS), University of Heidelberg, 69120 Heidelberg, Germany  <br> <sup>*</sup>Correspondence`:` kei.jokura @ exeter.ac.uk, gaspar.jekely @ cos.uni-heidelberg.de"
output:
  html_document:
    theme: lumen
  pdf_document:
    latex_engine: lualatex
    template: default
  word_document: default
geometry: left=0.8in,right=0.8in,top=0.8in,bottom=0.5in
mainfont: Arial
monofont: Times New Roman
documentclass: article
classoption: onecolumn
linestretch: 1.2
fontsize: 10pt
bibliography: references.bib
csl: elife.csl
editor_options: 
  markdown: 
    wrap: sentence
---

@@

## Key resources table

```{r echo=FALSE}
library(readxl)
key_resource_tale <- read_excel("key_resource_tale/key_resource_tale.xlsx")
df_key_resource_tale <- as.data.frame(key_resource_tale)
knitr::kable(df_key_resource_tale, format = "html", booktabs = TRUE)
```
